---
title: "RegMods Assignment"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary
Manual transmission better for MPG (miles per gallon) than automatic transmission. We did a multivariate regression to improve estimate of transmission types on MPG.

## Data Processing

```{r cars}
data(mtcars)

mtcars$cyl <- as.factor(mtcars$cyl)
mtcars$vs <- as.factor(mtcars$vs)
mtcars$gear <- factor(mtcars$gear)
mtcars$carb <- factor(mtcars$carb)
mtcars$am <- factor(mtcars$am,labels=c('Automatic','Manual'))
str(mtcars)
```

## EDA

Do a boxplot to examine car transmission types on mpg. We can say there is increase in mpg for manual transmission vs automatic transmission. Also, plot histogram to check for normal curve.

```{r eda}
par(mfrow = c(1, 2))
# Histogram with Normal Curve
x <- mtcars$mpg
h <- hist(x, breaks=10, col="salmon", xlab="Miles Per Gallon",
        main="Histogram of Miles per Gallon")

boxplot(mpg~am, data = mtcars,
        col = c("light blue", "light pink"),
        xlab = "Transmission",
        ylab = "Miles per Gallon",
        main = "MPG by Transmission Type")
```

## Hypotheses Testing

Seems that mean MPG of manual transmission cars is 7.24 MPGs higher than that of automatic transmission cars. We need to check whether this is a significant difference. Set alpha-value at 0.5 and run a t-test to find out.

```{r hypo test}
autoData <- mtcars[mtcars$am == "Automatic",]
manualData <- mtcars[mtcars$am == "Manual",]
t.test(autoData$mpg, manualData$mpg)
```

## Regression Analysis

```{r pairs}
pairs(mtcars)

data(mtcars)
sort(cor(mtcars)[1,])
```

Based on pairwise correlation of variables with mpg, we see that there is little linear correlation between mpg and the variables qsec, gear, and carb.

## Model building and selection

Model1 explains variation less (adjusted R Square: 0.3385) compared to Model2 (adjusted R Square: 0.8066). However, Model1's am variable give lower p-value (less than 0.05) whereas no variable in the model2 gives lower p-value than 0.05 (due to overfitting). Therefore, we use the step method to iterate over the variables and obtain the best model.

```{r models}
model1 <- lm(mpg~am, data = mtcars)
summary(model1)

model2 <- lm(mpg~., data = mtcars)
summary(model2)

best <- step(model2, direction = "both", trace = FALSE)
summary(best)
```

## Residual diagnostics

Residual are normally distributed and homoskedastic. So, we can report the estimates from our report.

```{r residuals}
par(mfrow = c(2,2))
plot(best)
```